---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

body{
  color:#dddddd;
  background-color: #000000;
  font-family: "Arial", cursive;
  letter-spacing: 1px;
  word-spacing: 2px;

}

h1,h2 {
  color : black;
  background-color: white;
  font-weight: "Bold";
  font-family: "Indie Flower", cursive;
  padding: 30px;
  text-align: center;
  text-shadow: 2px 2px 5px rgba(0, 0, 0, 0.5);

}

```

## Types of commuting transportation by age 

The purpose of this task is to demonstrate the relationship between the type of commuting transportation and the age of commuters

```{r fig.width = 6, fig.height = 4}
library(tidyverse)
logged_data <- read_csv(paste0("https://docs.google.com/spreadsheets",
"/d/e/2PACX-1vSm22IrT9r0H6mTjF-PlbhIhQbCKsC6ruOW8G2s_7raorH2YrdRFRr0wy",
"l4YVUyNG67YROGVoDFOV01/pub?output=csv"))

latest_data <- rename(logged_data)

a <- tibble(commuting = latest_data$`Do you use transportation for commuting?`, age = latest_data$`What is your age?`)
transporation_type = latest_data$`What is your type of transportation for commuting`
c <- tibble(transporation_type = latest_data$`What is your type of trasportation for commuting`, 
age = latest_data$`What is your age?`)


#Calculating the total number of respondents
num_people <- length(latest_data$`What is your age?`)

#Calculating the total number of respondents, excluding no commuters

total <- paste("The total number of respondents is", num_people, "people")

# Calculate the mean of the variable
num_commuter <- latest_data %>%
  count(`What is your type of transportation for commuting`, name = "count")

#Setting up a variable for commuting status of respondents
commuting = latest_data$`Do you use transportation for commuting?`

#Creating a bar chart between the number of respondents and the commuting status

a <- ggplot(latest_data, aes(x = commuting, fill = commuting)) +
  geom_bar(start = 'identity') +
  labs(title = "The number of commuters",
       subtitle = "Apprehending the number of commuters of my data",
       caption = "Source: Google form survery by Lucas Kang",
       x = "Commuting status",
       y = "The number of commuters") +
#Classifying the colour of each bar

  scale_fill_manual(values = c("No commuting" = "red",
                               "Yes" = '#33ddff'))
a
```

`r total`. 

The relationship between the type of commuting transportation and the number of commuters

```{r}
# Setting up a variable for transportation types
transporation_type = latest_data$`What is your type of transportation for commuting`
# Counting the number of respondents for each categories of transportation types
transportation_counts <- latest_data %>%
  group_by(`What is your type of transportation for commuting`) %>%
  summarise(count = n())

#Creating bar graph chart between the number of respondents and the transportation types

b <- ggplot(latest_data, aes(x = transporation_type, fill = transporation_type)) +
  geom_bar(start = 'identity') +
  labs(title = "Number of Respondents for Each Transportation Type",
       subtitle = "Comparing transportaion types for commuters",
       caption = "Source: Google form survery by Lucas Kang",
       x = "Transportaion types",
       y = "Number of commuters") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = c("Bus" = "red",
                               "Car (including Uber or taxi)" = 'yellow', "Motocycle" = 'green', "Walking" = 'blue'
                               ))
b

```

The relationship between the type of commuting transportation and the age of commuters

```{r}
#Calculating the average age of respondents of my data
average_age <- (sum(latest_data$`What is your age?`) / num_people) %>% round

average <- paste("The average age of respondents is", average_age)

#Calculating the maximum and minimum age value 
min_age <- min(latest_data$`What is your age?`, na.rm = TRUE)
max_age <- max(latest_data$`What is your age?`, na.rm = TRUE)

#Calculating the mean age for each transportation type excluding NA values
mean_age_by_transportation <- latest_data %>%
  group_by(`What is your type of transportation for commuting`) %>%
  summarise(mean_age = mean(`What is your age?`, na.rm = TRUE))

#Creating a bar chart between respondents' age and 
#the type of transportation for commuting

c %>%
  ggplot() +
  geom_bar(aes(x = age, fill = transporation_type)) +
  labs(title = "Transportaion types for commuting by age",
       subtitle = "Comparing transportaion types and age for commuters",
       caption = "Source: Google form survery by Lucas Kang",
       x = "Age (New Zealand Legal age)",
       y = "Transportation types") +
  scale_fill_manual(values = c("Bus" = "red",
                               "Car (including Uber or taxi)" = 'yellow', "Motocycle" = 'green', "Walking" = 'blue'
                               ))

```

The average age of the commuters in my data is `r average_age` including the maximum age value of `r max_age` and the minimum age value of `r min_age`.

